---
title: "Simple document"
author: Purnima Sharma
date: September 2020
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide 
---

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from , asterisk make it bold
a _normal distribution_:  , underscores make it italicized.
r code below starts with 3 back ticks and r in brackets (shortcut: alt + ctrl +i)

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too! And written text and code can be combined!
The mean is `r mean(samp)`.

# Section 3

## Data frame and plot

The code below creates a dataframe and generates a plot.

```{r plot_example, message FALSE}
library(tidyverse)

plot_df = tibble(
  x = rnorm(500, mean = 2, sd = 4),
  y = 3 - 4.2 * x + rnorm(500)
)

ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

This plot is really great!! It shows a linear relationship just as expected.

The data frame has `r nrow(plt_df)` rows.

Here is a list:
* This is my first list item
* Lists need at least two items
  * This list has a sub item
* Third list item

#### Table

col 1 | col 2
----- | -----
a     | b
c     | d



